\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-31 notes/2loopNLSM.tex
Added basic figs for the YM discussion.  Added color aliases for different colors (even though some of the names currently point to the same color).

\definecolor{nhpRed}{RGB}{161,0,0}
\definecolor{nhp4}{RGB}{203, 4, 31}
\definecolor{nhp3}{RGB}{244,99,30}
\definecolor{nhp2}{RGB}{255,159,0}
\definecolor{nhp1}{RGB}{48,152,152}
\definecolor{nhpBlue}{RGB}{0,100,144}
\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgreen}{RGB}{25,176,146}
\definecolor{hgreen1}{RGB}{175,230,175}
\definecolor{hblue}{RGB}{52,152,219}
\definecolor{hbluedark}{RGB}{36, 106, 160}
\definecolor{hblue1}{RGB}{255,255,166}
\definecolor{hred}{RGB}{216,83,117}
\definecolor{hreddark}{RGB}{151, 58, 81}
\definecolor{hred1}{RGB}{255,155,155}
\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgrey4}{RGB}{75,75,75}
\definecolor{hgrey5}{RGB}{50,50,50}
\definecolor{hgrey3}{RGB}{100,100,100}
\definecolor{hgrey}{RGB}{125,125,125}
\definecolor{hgrey2}{RGB}{125,125,125}
\definecolor{hgrey1}{RGB}{150,150,150}
\definecolor{hgrey0}{RGB}{175,175,175}
\definecolor{darkgreen}{RGB}{59,126,108}
\definecolor{nu-80}{RGB}{104, 076, 150}
\definecolor{nu-40}{RGB}{164, 149, 195}
\colorlet{ucp-color}{nu-40}

@@

\abstract{ For now, let's put the things we need to check/compute here in the abstract. 
\begin{enumerate}
\item Does our construction manifest all the cuts for the two-loop n-gon?
\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
\end{enumerate}
}

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing
constraints that directly involve such pathological diagrams.  That
leaves us with 14 non-pathological cubic diagrams on which to impose
maximal cuts and symmetries. \ace{Do we want the graphs for these?
  Doable in tikz, but would take some time, or I can dump nice-ish
  versions from mathematica}.  Doing so, we are left with AA total
parameters in the unrestricted ansatz and BB total in the
BDN-restricted ansatz.

@@

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,nhp4] (0,0) -- (c1);
      \draw[dashed,ultra thick,nhp4] (0,0) -- (c2);
      \draw[dashed,ultra thick,nhp4] (0,0) -- (c3);
      \draw[dashed,ultra thick,nhp4] (0,0) -- (c4);
      \draw[dashed,ultra thick,nhp4] (c5) -- ++(90:0.7*\cl);
      \node[fill=white,circle] (c) at (0,0) {};

  \end{tikzpicture},
\end{equation*}
as it is non-trivial and beyond the scope of this paper to define
exactly what such a cut and cut contribution means.  After discarding
these types of cuts, we are left with 8 unique cut topologies to
check.  Seven of these next-to-maximal cuts are consistent with the
kinematic Jacobi relations and symmetries.  Interestingly, the
``kissing triangles'' cut,
\begin{equation*}
  \KissingTriangles \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied.

@@

We now turn to exploring the use of non-local numerators to skirt the
incompatibility.  We expect that promoting the numerators to
sufficiently complicated rational functions of the momenta will
eventually produce a color-dual representation.  At worst one could
imagine diagram ``numerator'' functions where all possible propagators
of all diagrams appear in each diagram ``numerator's'' denominator, at
which point required contributions could be arbitrarily rearranged
between diagrams.  However, given the success of non-local loop
numerators in other contexts \cite{Square, WeinzierlBCJLagrangian,
  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl}, we hope that
only relatively tame additional denominators are required.

As a first attempt at such a non-local representation, we consider
allowing one factor each of $s$,$t$, or $u$ in the denominator of each
of the double-box and penta-triangle numerators, in addition to the
standard local ansatze.  In order to not over-count the local terms,
we restrict the non-local ansatze to only truly rational terms, \eg
for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
$x \propto s$.  Thus each basis diagram ansatz contains 114,422 terms
to start, 10,010 from the local terms and 34,804 from each of the
three non-local pieces.

\begin{itemize}
  \item Attempt at non-local.  Still have problems with cuts+syms+jacobi
  \end{itemize}

>>>>

\definecolor{nhpRed}{RGB}{161,0,0}
\definecolor{nhp4}{RGB}{203, 4, 31}
\definecolor{nhp3}{RGB}{244,99,30}
\definecolor{nhp2}{RGB}{255,159,0}
\definecolor{nhp1}{RGB}{48,152,152}
\definecolor{nhpBlue}{RGB}{0,100,144}
\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgreen}{RGB}{25,176,146}
\definecolor{hgreen1}{RGB}{175,230,175}
\definecolor{hblue}{RGB}{52,152,219}
\definecolor{hbluedark}{RGB}{36, 106, 160}
\definecolor{hblue1}{RGB}{255,255,166}
\definecolor{hred}{RGB}{216,83,117}
\definecolor{hreddark}{RGB}{151, 58, 81}
\definecolor{hred1}{RGB}{255,155,155}
\definecolor{cutred}{RGB}{219,56,49}
\definecolor{hgrey4}{RGB}{75,75,75}
\definecolor{hgrey5}{RGB}{50,50,50}
\definecolor{hgrey3}{RGB}{100,100,100}
\definecolor{hgrey}{RGB}{125,125,125}
\definecolor{hgrey2}{RGB}{125,125,125}
\definecolor{hgrey1}{RGB}{150,150,150}
\definecolor{hgrey0}{RGB}{175,175,175}
\definecolor{darkgreen}{RGB}{59,126,108}
\definecolor{nu-80}{RGB}{104, 076, 150}
\definecolor{nu-40}{RGB}{164, 149, 195}
\colorlet{ucp-color}{nhpBlue}
\colorlet{cut-color}{nhp4}
\colorlet{jacobi-color}{nhp4}
\colorlet{refl-color}{nhp4}

@@

\abstract{ For now, let's put the things we need to check/compute here in the abstract. 
\begin{enumerate}
\item Does our construction manifest all the cuts for the two-loop n-gon?
\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
    , \textcolor{cut-color}{\texttt{cut-color}},
    \textcolor{refl-color}{\texttt{refl-color}},and
    \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
    other colors so that we don't have to keep changing colors in
    multiple locations when we want to change diagram color schemes.
    I think I have updated all of the diagrams to use the
    correctly-named color, but haven't changed any of the backing
    colors for the names.}
\end{enumerate}
}

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing
constraints that directly involve such pathological diagrams.  That
leaves us with 14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc} on which to impose
maximal cuts and symmetries. \ace{Do we want the graphs for these?
  Doable in tikz, but would take some time, or I can dump nice-ish
  versions from mathematica}.  Doing so, we are left with AA total
parameters in the unrestricted ansatz and BB total in the
BDN-restricted ansatz.

\begin{figure}
  \foreach \x in {1,...,14}
  {
    \begin{minipage}{0.32\textwidth}
      \includegraphics[width=\textwidth]{temp-figs/nonpath-mc-\x.pdf}
    \end{minipage}
  }
  \caption{The 14 non-pathological maximal-cut diagrams}
  \label{fig:ym-mc}
\end{figure}

@@

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
      \node[fill=white,circle] (c) at (0,0) {};

  \end{tikzpicture},
\end{equation*}
as it is non-trivial and beyond the scope of this paper to define
exactly what such a cut and cut contribution means.  After discarding
these types of cuts, we are left with 8 unique cut topologies, shown
in \cref{fig:ym-nmc}, to check.  Seven of these next-to-maximal cuts
are consistent with the kinematic Jacobi relations and symmetries.
Interestingly, the ``kissing triangles'' cut,
\begin{equation*}
  \KissingTriangles \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied.

\begin{figure}
  \foreach \x in {1,...,8}
  {
    \begin{minipage}{0.32\textwidth}
      \includegraphics[width=\textwidth]{temp-figs/nonpath-nmc-\x.pdf}
    \end{minipage}
  }
  \caption{The 8 non-pathological next-to-maximal-cut diagrams}
  \label{fig:ym-nmc}
\end{figure}

@@

\iffalse
We now turn to exploring the use of non-local numerators to skirt the
incompatibility.  We expect that promoting the numerators to
sufficiently complicated rational functions of the momenta will
eventually produce a color-dual representation.  At worst one could
imagine diagram ``numerator'' functions where all possible propagators
of all diagrams appear in each diagram ``numerator's'' denominator, at
which point required contributions could be arbitrarily rearranged
between diagrams.  However, given the success of non-local loop
numerators in other contexts \cite{Square, WeinzierlBCJLagrangian,
  Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl}, we hope that
only relatively tame additional denominators are required.

As a first attempt at such a non-local representation, we consider
allowing one factor each of $s$,$t$, or $u$ in the denominator of each
of the double-box and penta-triangle numerators, in addition to the
standard local ansatze.  In order to not over-count the local terms,
we restrict the non-local ansatze to only truly rational terms, \eg
for the term $n_{\text{nl}}\sim \frac{x}{s}$ we drop all terms with
$x \propto s$.  Thus each basis diagram ansatz contains 114,422 terms
to start, 10,010 from the local terms and 34,804 from each of the
three non-local pieces.
\fi
